### 2020-12-17 slides_short/fsir.tex
more slides

\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Pareto}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.98)}, anchor={north east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Nr. Paramters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={15.305486448632008}, xmax={625.3313171144225}, xtick={{15.848931924611142,25.11886431509581,39.810717055349734,63.09573444801933,100.0,158.48931924611142,251.18864315095823,398.1071705534973}}, xticklabels={{$10^{1.2}$,$10^{1.4}$,$10^{1.6}$,$10^{1.8}$,$10^{2.0}$,$10^{2.2}$,$10^{2.4}$,$10^{2.6}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.005}, ymax={10000.0}, ytick={{0.01,0.1,1.0,10.0,100.0,1000.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={089ee56b-6822-4377-827c-374155ed22b5}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
            (105.0,0.05584966441816506)
            (102.0,0.04975238296092152)
            (109.0,0.05940020202500067)
            (89.0,2.294967031333799)
            (109.0,0.01674682323492209)
            (103.0,0.10720479779621425)
            (111.0,0.047378610574098125)
            (91.0,0.10379493048125163)
            (110.0,2.513624607833005)
            (104.0,0.05086478924822935)
            (109.0,0.11351618280207543)
            (108.0,0.4020253123624037)
            (110.0,0.07446102987541804)
            (105.0,0.11535032606585913)
            (111.0,0.18480906070431535)
            (98.0,0.20276032629175944)
            (107.0,0.08951349573643062)
            (102.0,0.04128707134536484)
            (111.0,0.08564751808207169)
            (101.0,0.3024196229705965)
            (134.0,0.0625994120602839)
            (123.0,0.07725887987692295)
            (137.0,0.0446213228734711)
            (133.0,0.3084188318399655)
            (133.0,0.01962266981062221)
            (134.0,0.10146607016990984)
            (138.0,0.06814314041036643)
            (126.0,0.1400125295960749)
            (138.0,467.4741755918939)
            (127.0,1.1166477896146412)
            (138.0,0.17714972309111646)
            (19.0,0.11922132709056152)
            (133.0,0.08769252229223219)
            (130.0,0.07793316024608679)
            (137.0,0.1718723416265335)
            (125.0,0.33914255094342527)
            (136.0,0.015348260495236497)
            (131.0,0.14565843998621403)
            (137.0,0.19446231157170504)
            (123.0,0.26589194567164826)
            (178.0,0.13602372744489552)
            (164.0,1.3096147548790622)
            (183.0,1.2001412178607553)
            (20.0,0.13777438440294185)
            (181.0,0.8479907542370899)
            (183.0,0.0950066129025234)
            (182.0,0.0973834969835291)
            (140.0,4.6045371868841265)
            (181.0,0.08489426529555413)
            (171.0,1.434207428800683)
            (182.0,0.03715339077893962)
            (172.0,0.22976469267521113)
            (179.0,0.021032926937894693)
            (174.0,0.12032695402812911)
            (183.0,0.1184679992516246)
            (167.0,0.19684607920197908)
            (179.0,0.07686867922650574)
            (173.0,2.5546282892181007)
            (182.0,2.568218715361108)
            (20.0,0.14201835288630793)
            (57.0,0.034130835764939665)
            (57.0,0.08573571106663361)
            (57.0,0.027468464787432298)
            (53.0,0.1845821255465333)
            (57.0,0.3145059229030894)
            (50.0,0.03924953982860379)
            (57.0,0.06856875980583756)
            (18.0,0.13408208779207065)
            (57.0,0.246120844440766)
            (57.0,0.04960174895763792)
            (57.0,2.4305662054492216e9)
            (49.0,0.19845525108383108)
            (57.0,0.10124427200601582)
            (57.0,723.2519398047787)
            (57.0,0.04868286562065639)
            (21.0,0.09182349525167144)
            (57.0,2.72184197085509)
            (57.0,0.02883792885224287)
            (57.0,0.05463115607163071)
            (47.0,3.4065463877724946)
            (83.0,0.0897939767464811)
            (73.0,0.13931869624662485)
            (82.0,0.2953775450777107)
            (78.0,0.18845400004232993)
            (83.0,0.03326786171772812)
            (81.0,0.03346088666911155)
            (84.0,0.021920164977564584)
            (29.0,0.13107584979633108)
            (83.0,0.025448977666601213)
            (83.0,0.052182247335789286)
            (84.0,0.03318537664315938)
            (19.0,0.11324273930491076)
            (83.0,0.049563710942017516)
            (82.0,0.05229073956836107)
            (84.0,0.936285586965232)
            (79.0,0.36352072822414827)
            (84.0,0.06743210142176875)
            (83.0,0.06069929189699635)
            (84.0,1.0402239808527012)
            (20.0,0.0863532735177328)
    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={fb8ade92-3de5-4181-955a-9068086f05cd}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
            (235.0,0.13357198945321846)
            (70.0,0.04461548817109118)
            (240.0,0.27826514621649645)
            (55.0,0.40610599113961626)
            (231.0,0.16842724844486784)
            (183.0,0.053126061241543406)
            (243.0,0.09279724868377123)
            (44.0,0.6219680679576621)
            (224.0,0.14673187421056033)
            (222.0,0.17126303810452492)
            (242.0,0.26732925740823366)
            (72.0,0.40406046468282036)
            (239.0,0.27881283308599)
            (215.0,0.08349271759735011)
            (242.0,0.2125101399226415)
            (32.0,0.5513286633867127)
            (235.0,0.22568337408398828)
            (206.0,0.09258343306049661)
            (243.0,0.20454040997137593)
            (26.0,0.5107297023521244)
            (323.0,0.3667902032609065)
            (106.0,0.04378510564953422)
            (346.0,0.16065746518529136)
            (41.0,0.4591112638861731)
            (338.0,0.16645620302038866)
            (329.0,0.0837772625628679)
            (343.0,0.14366152756083547)
            (43.0,0.6024946038819587)
            (331.0,0.18929036413010172)
            (287.0,0.33185148527249725)
            (348.0,0.04576725492168219)
            (40.0,0.5307735589972514)
            (333.0,0.25561466836673213)
            (267.0,0.08139063563463969)
            (348.0,0.2603533867117459)
            (42.0,0.485145599462851)
            (324.0,0.06458173214154204)
            (150.0,0.03822594080269291)
            (346.0,0.22772148021684693)
            (38.0,0.5349911168200644)
            (529.0,0.09246980203670312)
            (76.0,0.032150726839285076)
            (561.0,0.2953731709925806)
            (42.0,0.42435150858456305)
            (551.0,0.5658710399734437)
            (172.0,0.03671331385133575)
            (562.0,0.2247420272307935)
            (39.0,0.6093866677344313)
            (552.0,0.42285681275210707)
            (338.0,0.07585812329891815)
            (561.0,0.16916001531239544)
            (39.0,0.4801687797714871)
            (536.0,0.1460284576306947)
            (519.0,0.1674664372593216)
            (563.0,0.07034107539784748)
            (36.0,0.6153149633129895)
            (538.0,0.2901270824759899)
            (314.0,0.0894523538965804)
            (561.0,0.9493069230558913)
            (43.0,0.45231290229037063)
            (86.0,0.19904079876071654)
            (86.0,0.2474597369029254)
            (87.0,0.9661924012140722)
            (52.0,0.5183448216596367)
            (83.0,0.41163416709756745)
            (86.0,0.2018533637471545)
            (87.0,0.7338740990737738)
            (29.0,0.502255804939499)
            (85.0,0.24871677122634128)
            (79.0,0.47124624050445574)
            (87.0,0.3017981172481904)
            (34.0,0.4118665138102874)
            (86.0,0.46110233661130057)
            (81.0,0.34380752518935775)
            (87.0,0.592914605387025)
            (55.0,0.5340532094284938)
            (84.0,0.21982864921620568)
            (86.0,0.12593689360335356)
            (86.0,0.2490899738548067)
            (30.0,0.3888134391760499)
            (149.0,0.155251101357749)
            (131.0,0.055439107403504)
            (155.0,0.12238978551321686)
            (35.0,0.43098325658284026)
            (154.0,0.1394374093998332)
            (152.0,0.2297799184953769)
            (155.0,0.15759694151794004)
            (39.0,0.5057258031699502)
            (154.0,0.3922494485884269)
            (153.0,0.3902229654498584)
            (156.0,0.2773388179874096)
            (43.0,0.5416488514754519)
            (152.0,0.2540652840489718)
            (152.0,0.11832827918668122)
            (154.0,0.11410277669310671)
            (45.0,0.5469697488849031)
            (151.0,0.1870216675213049)
            (127.0,0.16707232055495033)
            (154.0,0.8019823908524971)
            (52.0,0.5113011726127454)
    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={a4a2407a-9d13-4d5f-9806-f4dc789913ff}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
            (75.0,3.147945165083429)
            (73.0,0.7787622330875555)
            (75.0,14.274696485077706)
            (72.0,1.0547043767865791)
            (75.0,3.332024981183407)
            (73.0,0.8054592789691524)
            (75.0,1.9717984455866802)
            (30.0,0.3567713595345774)
            (74.0,1.3257338505548062)
            (71.0,0.454412627271946)
            (75.0,199.32322467686308)
            (75.0,1.0895748631691455)
            (75.0,2.4040986461550835)
            (75.0,30.945783537221924)
            (75.0,1.3655781266539022)
            (72.0,1.7771060355248247)
            (75.0,2.095095365942199)
            (74.0,1.2957150765737162)
            (75.0,10.287194966343153)
            (71.0,23.823930630622364)
            (91.0,2.4310322835821725)
            (90.0,2.03837213281791)
            (93.0,18.48678688820552)
            (18.0,0.1828119186366187)
            (93.0,1.402802143535598)
            (93.0,0.5216804362331351)
            (93.0,344.95675624956914)
            (17.0,0.028392317708999436)
            (93.0,0.5279417818890894)
            (92.0,2.279971972737263)
            (93.0,1.6171895486111396)
            (87.0,0.9929110131500897)
            (92.0,1.6970363177778334)
            (88.0,1.281239828889679)
            (93.0,1.9682814650085763)
            (90.0,1.0443588384128824)
            (93.0,1.4672964427212034)
            (93.0,2.512126815083123)
            (93.0,1.7528157502014407e27)
            (17.0,0.042776379040499156)
            (123.0,292782.19801080116)
            (114.0,0.8319858220508034)
            (122.0,38.36679799718143)
            (119.0,4.247901992170559)
            (123.0,2.1603952895878047)
            (123.0,1.612179389285352)
            (123.0,2.1315469624808055e8)
            (120.0,2.863381885496416)
            (123.0,1.5701579511267307)
            (115.0,1.1995883679712909)
            (122.0,0.8442486879600574)
            (107.0,1.4996647965557675)
            (123.0,43.27286005493181)
            (123.0,0.22240221552099876)
            (123.0,1.724556189521123)
            (123.0,0.7600881434640848)
            (123.0,1.55953539967718)
            (122.0,2.5016970428713385)
            (122.0,125.83729920965449)
            (119.0,1.474402129759871)
            (39.0,1.6787168071085867)
            (38.0,23.286011001150722)
            (39.0,1.8524442120647987e6)
            (39.0,1.1819811023887494)
            (38.0,25.653816244212006)
            (39.0,7.724620004876016)
            (39.0,1.5998738392072849)
            (39.0,230.55843153298235)
            (38.0,35.384317652871445)
            (39.0,18.021070189844696)
            (39.0,195.47077720096976)
            (39.0,160.86609736256958)
            (39.0,3.0592725712776643)
            (39.0,4.398153803012362)
            (39.0,1.1590218432565333)
            (17.0,0.035424442595674274)
            (38.0,4162.440925088575)
            (39.0,40.27926776330599)
            (39.0,2.6373813625877043)
            (39.0,9.740619004230942)
            (57.0,0.8097482769396408)
            (57.0,0.8683241511330079)
            (57.0,0.6548577323997611)
            (57.0,18.271264624639596)
            (57.0,0.8110250229754907)
            (57.0,1.0118191812875524e19)
            (57.0,1166.0668083720273)
            (54.0,24.255595170101138)
            (57.0,2.4197291464377434e17)
            (57.0,25.939711745446342)
            (57.0,411.43443310327984)
            (54.0,25.852674031372572)
            (57.0,1.0362054731778492)
            (57.0,1.0072691225003283e14)
            (56.0,62.4551625376836)
            (47.0,0.3358689620078998)
            (57.0,2.1657544482083853)
            (57.0,1.253110778534678)
            (57.0,2.6027300344473447)
            (57.0,26.29584591974179)
    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={6fca2f50-6519-44f2-b9d9-640264e75dcd}, draw opacity={1.0}, line width={2}, dashed]
            (26.0,0.5107297023521244)
            (30.0,0.3888134391760499)
            (70.0,0.04461548817109118)
            (76.0,0.032150726839285076)
            (172.0,0.03671331385133575)
            (348.0,0.04576725492168219)
            (563.0,0.07034107539784748)
    \addlegendentry {Dense}
    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={4df2801f-27fe-4ea1-9f00-dbdbe35d4500}, draw opacity={1.0}, line width={2}, solid]
            (57.0,2.4305662054492216e9)
            (18.0,0.13408208779207065)
            (20.0,0.0863532735177328)
            (57.0,0.027468464787432298)
            (109.0,0.01674682323492209)
            (136.0,0.015348260495236497)
            (179.0,0.021032926937894693)
    \addlegendentry {NPU}
    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={23f3a274-9dd0-40ba-b4c3-9bf7970f58c1}, draw opacity={1.0}, line width={2}, dashdotted]
            (39.0,1.8524442120647987e6)
            (17.0,0.042776379040499156)
            (17.0,0.028392317708999436)
            (123.0,0.22240221552099876)
    \addlegendentry {RealNPU}
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={SIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]

>>>>

\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={fSIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
